---
title: "Predict Stopping distance based on Speed of in 1920"
author: "Huong Tran"
date: "1/18/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introdution:
- This is an assignment about building Shiny app of the course Developing Data Products.
- I am using **cars** dataset.
- **Note**: This dataset were recorded in the 1920s, which may yeild difference 
in today cars. 

## About **cars** dataset:
```{r, echo=FALSE, include = FALSE}
library(ggplot2)
library(datasets)
data(cars)
```
Now, we will take a look at the dataset:
```{r}
head(cars)
```
```{r}
paste("The speed range from ", range(cars$speed)[1], "to", range(cars$speed)[2])
```
```{r}
paste("The distance range from ", range(cars$dist[1]), "to", range(cars$dist)[2])
```

## Scatterplot:
```{r, echo= FALSE, message = FALSE}
g <- ggplot(data = cars, aes(speed, dist))
g + geom_point() + geom_smooth(method = "lm") + labs(main = "Scatter plot and least square regression line")

```
## Linear Model:
Using Least Square method:
```{r, message = FALSE}
model <- lm(dist ~ speed, data = cars)
summary(model)
```
## Summary:
- $p$-value of $F$-test is small, which mean the model is useful to predict the  
stopping distance based on the speed.
- However, $R^2$ = 0.6511, which means only $65.11\%$ of stopping distance can be 
explained by this model.



